My wonderful paper

### 2024-12-05 _manuscript/_tex/index.tex
small changes

@@

\subsection{Unit tests}\label{unit-tests}

Why develop unit tests in software engineering? Because it is difficult
to predict the outcome of a program, especially when the program is
complex. Because the loss associated with a program failure is costly.

Existing tools for checks in data analysis including those check for
data quality and model diagnostics. In software development,

\begin{itemize}
\tightlist
\item
  the \texttt{testthat} package \citep{testthat} provides the
  infrastructure for testing R code. It allows users to write unit tests
  for functions and packages.
\item
  The \texttt{assertthat} package \citep{assertthat} helps to write
  assertion statements that are supposed to be true at a certain point
  in the code for defensive programming.
\end{itemize}

\section{xxxxx (not analysis plan)}\label{sec-plan}

\subsection{Framing checks into unit
tests}\label{framing-checks-into-unit-tests}

@@

Yet, making them explicit is crucial for 1) helping junior researchers
interpret results and diagnose the unexpected, 2) providing checkpoints
that support independent replication or application of methods to new
data, 3) aligning assumption across researchers from different
backgrounds.

>>>>

\section{Analysis validation checks}\label{sec-plan}

\subsection{Framing expectations as
checks}\label{framing-expectations-as-checks}

@@

@@

Yet, making them explicit is crucial for

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  helping junior researchers interpret results and diagnose the
  unexpected,
\item
  providing checkpoints that support independent replication or
  application of methods to new data, and
\item
  aligning assumption across researchers from different backgrounds.
\end{enumerate}

### 2024-12-05 index.qmd
small changes

@@

## Unit tests

Why develop unit tests in software engineering? Because it is difficult to predict the outcome of a program, especially when the program is complex. Because the loss associated with a program failure is costly.

Existing tools for checks in data analysis including those check for data quality and model diagnostics. In software development,

-   the `testthat` package [@testthat] provides the infrastructure for testing R code. It allows users to write unit tests for functions and packages.
-   The `assertthat` package [@assertthat] helps to write assertion statements that are supposed to be true at a certain point in the code for defensive programming.

# xxxxx (not analysis plan) {#sec-plan}

## Framing checks into unit tests

<!-- The analysis plan described in this paper should be differentiated from the pre-specifies analysis plan document often used in biostatistics to specifies the hypothesis, data collection mechanism, statistical procedures etc of randomized experiments.  -->

@@

Yet, making them explicit is crucial for 1) helping junior researchers interpret results and diagnose the unexpected, 2) providing checkpoints that support independent replication or application of methods to new data, 3) aligning assumption across researchers from different backgrounds.

>>>>

# Analysis validation checks {#sec-plan}

## Framing expectations as checks

@@

@@

Yet, making them explicit is crucial for

  1) helping junior researchers interpret results and diagnose the unexpected, 
  2) providing checkpoints that support independent replication or application of methods to new data, and
  3) aligning assumption across researchers from different backgrounds.
